Reading Notes

### 2020-08-26 2pd.tex
coarse graining -> coarse-graining

%%create models for new opv compounds>
In order to model these OPV polymer systems on relevant length scales, it is necessary to develop new coarse-grained models.
A flexible and efficient coarse graining scheme will simplify the process of mapping and parameterizing these coarse-grained elements. %% reword?

%%gain insight into the limits of coarse graining>
The flexibility of specifying a mapping will allow for the comparison of multiple mappings which may provide insight into the features of an OPV which govern its self-assembly and the limits of coarse-grained models.
Currently there is no agreed-upon ``best'' scheme for a coarse-grained mapping operator.
By making a simple and easy-to-use coarse graining tool, many mapping operators can be tested and the limits of a minimal model can be probed.
%% What is the minimum structure needed to represent a complex molecule? %% reword? omit?

@@

%%<what are the limits of atomistic md?>
Even with the simplifications of MD, we are still not able to simulate many systems efficiently on relevant length scales.
Therefore we can use a technique called coarse graining to increase the length and time scales we can examine.
%%<segue to why we need CG models>

@@

Coarse graining refers to grouping atoms in a structure into a ``super atom'' and using an effective potential to represent the resulting coarse-grained site.
Coarse grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models by abstracting away irrelevant degrees of freedom.
%%<how do cg models let us access long length/time??>
Similarly to how we don't need to look at the working of a plant cell to understand the growth of a forest, we don't need to consider atomic level properties when we are interested in the bulk morphology\cite{Muller-Plathe2002}.
The heart of coarse graining is the removal of degrees of freedom. 
This effective potential used to represent the reduced system results in a smoothed free energy landscape. 
Processes which may have taken many time steps in an all atom simulation can take fewer time steps in a coarse simulation\cite{Berendsen2010}.
Due to their long length and time scales, coarse-grained models are ideal for examining polymer properties\cite{Gartner2019a}.
It is too big and too slow and also just a bad idea to simulate huge boxes of atomistic polymers.
Even if the simulation was to complete, there would be too much information to process accurately. 
Coarse graining allows scientists to \textit{focus} their experiments\cite{Baschnagel2000}.

@@

%%<segue from automated creation of forcefields to...>
%%<mapping operator has to be decided by hand> <is this section too big?>
Part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator.
A mapping operator defines which atoms are grouped into a ``super atom'' represented by one coarse-grained site and where the site is placed relative to the atom group.
Mapping operators are chosen based on the desired resolution of the coarse-grained system and the information to be extracted.
A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together; this is the method used in the notable MARTINI force field\cite{Marrink2007}.
In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
When parameterizing a new molecule for the MARTINI method, a user must pick a mapping and then compare the chemical structure of the resulting sites to those which have already been parameterized; a process which is time consuming and error prone\cite{martini-tutorial}.
The published tutorial recommends searching through existing MARTINI topologies to find similar structures and then manually editing them to fit the new molecule.
Whether the structure is similar then is based on the user's chemical knowledge, judgement, and intuition.
%%The MARTINI force field was first designed for lipids, further parameterization for proteins and nuclei acids has since been added, and it has been shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.%%<cite
Many other mapping schemes also rely on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend? What groups have the most dominant interactions in this structure). %%<cite any model where rings are one site><cite dna cg model>).
As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
There have been efforts to create algorithms for automating the process of deciding which atoms are grouped in a ``super atom''.
One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the ``best'' mapping by comparing the difference between the mapped RDF and velocity autocorrelation function\cite{Chakraborty2018b}.
Another uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the ``expert'' mapping chosen using chemical intuition reliably\cite{Li2020}. 
A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.
%%<how cg potentials have been attained> 
Deciding on a mapping operator is one part of creating a coarse-grained model, the second step is to create an effective potential for the site.

@@

%% Objectives are like steps along the way
%% objectives should be
% 1. goal of the step
% 2. how to do the step
% how doing this achieves the goal
%% how to coarse-grained reproducibly
\subsection*{Objective 1: Develop a generalized toolset for coarse graining and performing simulations of novel molecules for organic photovoltaics}
% mapping
% ff creation
% infrastructure: porting ff to engine
In order to model the morphologies of new OPV chemistries, we need a simple way to generate novel coarse-grained models.
This objective consists of three steps:
\begin{enumerate}
    \item {Create a tool that uses a mapping operator to go from atomistic to coarse-grained structure}
    \item {Use the mapped coarse-grained structure to parameterize a force field using MSIBI}
    \item {Develop the infrastructure to port this force field to a simulation engine}
\end{enumerate}
A minimum working example of this coarse-grained mapping tool has been completed. %% cite grits, cg-tutorial
However, it will still need to be tested with many more compounds and mapping operators.
This package uses the chemical file format parsing and scriptable structure building capabilities of mbuild coupled with the SMARTS/SMILES string matching of the openbabel package to generate coarse-grained structures mapped onto their atomistic counterparts with only a SMARTS string from the user.
These coarse-grained structures mapped to an atomistic target can then be used in an MSIBI workflow to obtain an effective potential.
A minimum working example of an MSIBI tool has also been started; %https://bitbucket.org/cmelab/msibi_tests/src/master/ do i even mention this?
although the hands-on experience with MSIBI was useful to me in getting a better understanding for the process, I think for future, I will build off an existing MSIBI code. %%https://github.com/mosdef-hub/msibi
The force field obtained using MSIBI will then be used to run a simulation of a novel coarse-grained model.
Therefore decisions about how to carry the forcefield information into a simulation engine will need to be made.
Here we will focus on HOOMD, but transferrability among simulation engines will be a goal.
\textbf{Completion Critera:} Force fields and initial configurations usable with HOOMD-Blue that enable the equilibration of: 5 polymers, 5 fullerene derivatives, and 5 ITIC derivatives. 
% workflow is complete when we can cg these chemistries
% use ff in different sim engines

@@

In order to calculate the charge transport of a coarse-grained representation of a morphology, we need to be able to regain the atomic positions.
Given an equilibrated coarse-grained trajectory, we can reintroduce the atomistic degrees of freedom by using the same SMARTS mappings used for coarse graining.
The chemistries specified by the SMARTS strings will be mapped onto the centers of the CG sites and then equilibrated in a short MD run using the atomistic force field with an additional position restraint to maintain the structure. 
I have developed a minimum working example of this backmapping process, %% cite grits
however, the specification of how the backmapped atomistic structures are bonded is still not intuitive for the user to specify and I am not sure yet how to make it better.
The backmapping workflow will be considered complete when it can backmap a test set of 25 common OPV chemistries from all possible mappings.

@@

Once Objectives 1 and 2 are complete, the next step will be putting them to use to investigate new OPV compounds.
Currently, I have not found CG models for many NFA compounds (e.g, ITIC). %% I found this paper~\cite{Meng2019} that claims to do CGMD with PTB7 ITIC but the details are hidden in the SI and seem fishy. seems like they use IBI but they dont say how they got their target distributions.
A simple, useable coarse graining tool will be helpful for determining the best mapping operator to use for these OPV compounds.
To help organize the dataspace of the large parameter sweep, I plan to use the signac package to manage an ever-changing workspace.
This will help easily and efficiently test out different mappings and ``processing'' conditions.

@@

\begin{enumerate}
    \item {\textbf{Gain insight into the limits of coarse-graining}}
        This work will probe the limits of coarse graining to understand the minimal model necessary to represent different OPV chemistries.
    \item {\textbf{Understand the interactions which guide BHJ self assembly}} 
        This work will test a variety of different OPV compounds. 
        Comparing the results may provide understanding into which moeities, intermolecular interactions, or processing conditions result in the morphology with the highest charge transport.
    \item {\textbf{Understand the mapping operator}}
        This work will test whether using a chemical string format (SMARTS/SMILES) to specify the atomistic to coarse-grained site mapping is a viable alternative to other methods. 
        Using SMARTS/SMILES strings allows a user to more easily and intuitively specify a mapping.
        If specifying a mapping is easier, a user may be more willing to try out a greater number of different mappings.
        This would allow for the comparison of a system parameterized with different mapping operators.
    \item {\textbf{Benefits of Transferrable, Reproducible, Usable, Extensible research}} %%what am i trying to say here?
        Does making science easier/more understandable make it better? %more reproducible? curb cuts
        If parameterizing a coarse-grained force field is easier and more approachable, it would open up more possibilities for trying different mapping schemes or different structural or thermodynamic targets rather than sticking to an existing force field.
        Better coarse-grained models could result in more accurate and efficient simulation of large length scale systems.
\end{enumerate}

@@

%%<what's going to be hard?> 
Although minimum working examples have been developed for botht the coarse graining and backmapping packages, I still expect to struggle when mapping new compounds.
Sometimes the SMARTS/SMILES mapping won't work without careful choice of sites.
This can be a little frustrating but is still preferrable to having to manually specify the mapping of each atom.
At least the reasons that a SMARTS mapping fails are usually understandable (e.g., the order of the sites matters) or chemically sensible (e.g., one SMILES string may contain another --- just as one chemical moeity may be composed of more submoeities). %%<this is a word?>)

It may also be difficult to find a good coarse graining scheme for the NFA compounds. 
These compounds are often composed of large planar backbones with floppy side chains.
Finding a suitable mapping to represent both aspects may be difficult.

>>>>

%%create models for new opv compounds>
In order to model these OPV polymer systems on relevant length scales, it is necessary to develop new coarse-grained models.
A flexible and efficient coarse-graining scheme will simplify the process of mapping and parameterizing these coarse-grained elements. %% reword?

%%gain insight into the limits of coarse-graining>
The flexibility of specifying a mapping will allow for the comparison of multiple mappings which may provide insight into the features of an OPV which govern its self-assembly and the limits of coarse-grained models.
Currently there is no agreed-upon ``best'' scheme for a coarse-grained mapping operator.
By making a simple and easy-to-use coarse-graining tool, many mapping operators can be tested and the limits of a minimal model can be probed.
%% What is the minimum structure needed to represent a complex molecule? %% reword? omit?

@@

%%<what are the limits of atomistic md?>
Even with the simplifications of MD, we are still not able to simulate many systems efficiently on relevant length scales.
Therefore we can use a technique called coarse-graining to increase the length and time scales we can examine.
%%<segue to why we need CG models>

@@

Coarse graining refers to grouping atoms in a structure into a ``super atom'' and using an effective potential to represent the resulting coarse-grained site.
Coarse grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models by abstracting away irrelevant degrees of freedom.
%%<how do cg models let us access long length/time??>
Similarly to how we don't need to look at the working of a plant cell to understand the growth of a forest, we don't need to consider atomic level properties when we are interested in the bulk morphology\cite{Muller-Plathe2002}.
The heart of coarse-graining is the removal of degrees of freedom. 
This effective potential used to represent the reduced system results in a smoothed free energy landscape. 
Processes which may have taken many time steps in an all atom simulation can take fewer time steps in a coarse simulation\cite{Berendsen2010}.
Due to their long length and time scales, coarse-grained models are ideal for examining polymer properties\cite{Gartner2019a}.
It is too big and too slow and also just a bad idea to simulate huge boxes of atomistic polymers.
Even if the simulation was to complete, there would be too much information to process accurately. 
Coarse graining allows scientists to \textit{focus} their experiments\cite{Baschnagel2000}.

@@

%%<segue from automated creation of forcefields to...>
%%<mapping operator has to be decided by hand> <is this section too big?>
Part of coarse-graining that is not yet automated is choosing a mapping scheme or a mapping operator.
A mapping operator defines which atoms are grouped into a ``super atom'' represented by one coarse-grained site and where the site is placed relative to the atom group.
Mapping operators are chosen based on the desired resolution of the coarse-grained system and the information to be extracted.
A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together; this is the method used in the notable MARTINI force field\cite{Marrink2007}.
In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
When parameterizing a new molecule for the MARTINI method, a user must pick a mapping and then compare the chemical structure of the resulting sites to those which have already been parameterized; a process which is time consuming and error prone\cite{martini-tutorial}.
The published tutorial recommends searching through existing MARTINI topologies to find similar structures and then manually editing them to fit the new molecule.
Whether the structure is similar then is based on the user's chemical knowledge, judgement, and intuition.
%%The MARTINI force field was first designed for lipids, further parameterization for proteins and nuclei acids has since been added, and it has been shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.%%<cite
Many other mapping schemes also rely on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend? What groups have the most dominant interactions in this structure). %%<cite any model where rings are one site><cite dna cg model>).
As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
There have been efforts to create algorithms for automating the process of deciding which atoms are grouped in a ``super atom''.
One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the ``best'' mapping by comparing the difference between the mapped RDF and velocity autocorrelation function\cite{Chakraborty2018b}.
Another uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the ``expert'' mapping chosen using chemical intuition reliably\cite{Li2020}. 
A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.
%%<how cg potentials have been attained> 
Deciding on a mapping operator is one part of creating a coarse-grained model, the second step is to create an effective potential for the site.

@@

%% Objectives are like steps along the way
%% objectives should be
% 1. goal of the step
% 2. how to do the step
% how doing this achieves the goal
%% how to coarse-grained reproducibly
\subsection*{Objective 1: Develop a generalized toolset for coarse-graining and performing simulations of novel molecules for organic photovoltaics}
% mapping
% ff creation
% infrastructure: porting ff to engine
In order to model the morphologies of new OPV chemistries, we need a simple way to generate novel coarse-grained models.
This objective consists of three steps:
\begin{enumerate}
    \item {Create a tool that uses a mapping operator to go from atomistic to coarse-grained structure}
    \item {Use the mapped coarse-grained structure to parameterize a force field using MSIBI}
    \item {Develop the infrastructure to port this force field to a simulation engine}
\end{enumerate}
A minimum working example of this coarse-grained mapping tool has been completed. %% cite grits, cg-tutorial
However, it will still need to be tested with many more compounds and mapping operators.
This package uses the chemical file format parsing and scriptable structure building capabilities of mbuild coupled with the SMARTS/SMILES string matching of the openbabel package to generate coarse-grained structures mapped onto their atomistic counterparts with only a SMARTS string from the user.
These coarse-grained structures mapped to an atomistic target can then be used in an MSIBI workflow to obtain an effective potential.
A minimum working example of an MSIBI tool has also been started; %https://bitbucket.org/cmelab/msibi_tests/src/master/ do i even mention this?
although the hands-on experience with MSIBI was useful to me in getting a better understanding for the process, I think for future, I will build off an existing MSIBI code. %%https://github.com/mosdef-hub/msibi
The force field obtained using MSIBI will then be used to run a simulation of a novel coarse-grained model.
Therefore decisions about how to carry the forcefield information into a simulation engine will need to be made.
Here we will focus on HOOMD, but transferrability among simulation engines will be a goal.
\textbf{Completion Critera:} Force fields and initial configurations usable with HOOMD-Blue that enable the equilibration of: 5 polymers, 5 fullerene derivatives, and 5 ITIC derivatives. 
% workflow is complete when we can cg these chemistries
% use ff in different sim engines

@@

In order to calculate the charge transport of a coarse-grained representation of a morphology, we need to be able to regain the atomic positions.
Given an equilibrated coarse-grained trajectory, we can reintroduce the atomistic degrees of freedom by using the same SMARTS mappings used for coarse-graining.
The chemistries specified by the SMARTS strings will be mapped onto the centers of the CG sites and then equilibrated in a short MD run using the atomistic force field with an additional position restraint to maintain the structure. 
I have developed a minimum working example of this backmapping process, %% cite grits
however, the specification of how the backmapped atomistic structures are bonded is still not intuitive for the user to specify and I am not sure yet how to make it better.
The backmapping workflow will be considered complete when it can backmap a test set of 25 common OPV chemistries from all possible mappings.

@@

Once Objectives 1 and 2 are complete, the next step will be putting them to use to investigate new OPV compounds.
Currently, I have not found CG models for many NFA compounds (e.g, ITIC). %% I found this paper~\cite{Meng2019} that claims to do CGMD with PTB7 ITIC but the details are hidden in the SI and seem fishy. seems like they use IBI but they dont say how they got their target distributions.
A simple, useable coarse-graining tool will be helpful for determining the best mapping operator to use for these OPV compounds.
To help organize the dataspace of the large parameter sweep, I plan to use the signac package to manage an ever-changing workspace.
This will help easily and efficiently test out different mappings and ``processing'' conditions.

@@

\begin{enumerate}
    \item {\textbf{Gain insight into the limits of coarse-graining}}
        This work will probe the limits of coarse-graining to understand the minimal model necessary to represent different OPV chemistries.
    \item {\textbf{Understand the interactions which guide BHJ self assembly}} 
        This work will test a variety of different OPV compounds. 
        Comparing the results may provide understanding into which moeities, intermolecular interactions, or processing conditions result in the morphology with the highest charge transport.
    \item {\textbf{Understand the mapping operator}}
        This work will test whether using a chemical string format (SMARTS/SMILES) to specify the atomistic to coarse-grained site mapping is a viable alternative to other methods. 
        Using SMARTS/SMILES strings allows a user to more easily and intuitively specify a mapping.
        If specifying a mapping is easier, a user may be more willing to try out a greater number of different mappings.
        This would allow for the comparison of a system parameterized with different mapping operators.
    \item {\textbf{Benefits of Transferrable, Reproducible, Usable, Extensible research}} %%what am i trying to say here?
        Does making science easier/more understandable make it better? %more reproducible? curb cuts
        If parameterizing a coarse-grained force field is easier and more approachable, it would open up more possibilities for trying different mapping schemes or different structural or thermodynamic targets rather than sticking to an existing force field.
        Better coarse-grained models could result in more accurate and efficient simulation of large length scale systems.
\end{enumerate}

@@

%%<what's going to be hard?> 
Although minimum working examples have been developed for both the coarse-graining and backmapping packages, I still expect to struggle when mapping new compounds.
Sometimes the SMARTS/SMILES mapping won't work without careful choice of sites.
This can be a little frustrating but is still preferrable to having to manually specify the mapping of each atom.
At least the reasons that a SMARTS mapping fails are usually understandable (e.g., the order of the sites matters) or chemically sensible (e.g., one SMILES string may contain another --- just as one chemical moeity may be composed of more submoeities). %%<this is a word?>)

It may also be difficult to find a good coarse-graining scheme for the NFA compounds. 
These compounds are often composed of large planar backbones with floppy side chains.
Finding a suitable mapping to represent both aspects may be difficult.
